Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2016-01-19 WSSSPE3/report/wg_appendix_metrics.tex
fix latex so document compiles
Small changes and line breaks
Fix typos
Appendix H: Line breaks. One question.
removing question

\begin{itemize}
\item Gabrielle Allen -- National Center for Supercomputing Applications
\item Emily Chen -- University of Illinois at Urbana-Champaign
\item Neil Chue Hong -- U.K. Software Sustainability Institute
\item Ray Idaszak -- RENCI, University of North Carolina at Chapel Hill
\item Iain Larmou -- Engineering and Physical Sciences Research Council
\item Bernie Randles -- University of California, Los Angeles
\item Dan Sellars -- Canarie
\item Fraser Watson -- National Solar Observatory
\end{itemize}

@@

The following summary of the group's discussion represents the Useful Metrics for Scientific Software working group's discussion during the WSSSPE3 workshop. The group discussion began by agreeing on the common purpose of creating a set of guidance giving examples of specific metrics for the success of scientific software in use, why they were chosen, what they are useful to measure, and any challenges and pitfalls; then publish this as a white paper.  The group discussed many questions related to useful metrics for scientific software as follows:

\begin{itemize}

@@

\item
Can we fit metrics into a common template (i.e. for collection, for description)

@@

\item
Number of users could be affected by other metrics e.g. by accessibility

@@

\begin{itemize}
\item
        Ideal situation is the absolute minimum, so that people can decide on their own what the cost versus usefulness tipping point is
\end{itemize}

@@

\item
        Where should funders place funding for best impact (e.g. funding two-star software versus three-star) and where there are gaps

@@

\smallskip
\noindent
Next, a roadmap for how to proceed was discussed including creating a set of milestones and tasks as follows:

\begin{itemize}
\item
Can we create a roadmap and milestones for this activity

@@

\begin{itemize}
\item
                Ask SI2 PIs to say what metrics they said they would use (copied from proposal)

\item
                Ask SI2 PIs what numbers they reported

@@

\item
Coordination (mail communication, info page etc), via WSSSPE github or?

@@

The following items were discussed as a roadmap for the production of a white paper:

\begin{enumerate}
\item
October -- November 2015: IRB paperwork as appropriate completed (Gabrielle Allen and Emily Chen)

@@

\begin{enumerate}
\item
        Piggyback on planning for 2016 NSF SI2 PIs meeting to be held Feb 16-17, 2016
\end{enumerate}

>>>>

\begin{itemize}
\item Gabrielle Allen -- University of Illinois at Urbana-Champaign
\item Emily Chen -- University of Illinois at Urbana-Champaign
\item Neil Chue Hong -- U.K. Software Sustainability Institute
\item Ray Idaszak -- RENCI, University of North Carolina at Chapel Hill
\item Iain Larmou -- Engineering and Physical Sciences Research Council
\item Bernie Randles -- University of California, Los Angeles
\item Dan Sellars -- Canarie
\item Fraser Watson -- National Solar Observatory
\end{itemize}

@@

The following summary of the group's discussion represents the Useful Metrics
for Scientific Software working group's discussion during the WSSSPE3 workshop.
The group discussion began by agreeing on the common purpose of creating a set
of guidance giving examples of specific metrics for the success of scientific
software in use, why they were chosen, what they are useful to measure, and any
challenges and pitfalls; then publish this as a white paper. The group discussed
many questions related to useful metrics for scientific software as follows:
\begin{itemize}

@@

\item
Can we fit metrics into a common template (i.e., for collection, for description)

@@

\item
Number of users could be affected by other metrics e.g., by accessibility

@@

\begin{itemize}
\item
Ideal situation is the absolute minimum, so that people can decide on their own
what the cost versus usefulness tipping point is

@@

\item
        Where should funders place funding for best impact (e.g., funding two-star software versus three-star) and where there are gaps

@@

\smallskip
\noindent
Next, a roadmap for how to proceed was discussed including creating a set of
milestones and tasks as follows:
\begin{itemize}
\item
Can we create a roadmap and milestones for this activity

@@

\begin{itemize}
\item
Ask SI2 PIs to say what metrics they said they would use (copied from proposal)
\item
                Ask SI2 PIs what numbers they reported

@@

\item
Coordination (mail communication, info page etc), via WSSSPE GitHub or other?

@@

The following items were discussed as a roadmap for the production of a white
paper:
\begin{enumerate}
\item
October -- November 2015: IRB paperwork as appropriate completed (Gabrielle
Allen and Emily Chen)

@@

\begin{enumerate}
\item
Piggyback on planning for 2016 NSF SI2 PIs meeting to be held Feb 16-17, 2016
